WunderPass-White-Paper

### 2022-03-25 [B][Pools]/[Pools].tex
WPT REFACTORINGS

\subsection{Pool-Liquidierung}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Liquidierung]}    % binde die Datei '[Pools][Liquidierung].tex' ein

@@

\subsection{Pool-Economics}
\vspace{0.3cm}
%\input{[B][Pools]/[Pools][Economic]}    % binde die Datei '[Pools][Economic].tex' ein
\input{[Pools][Economic]}

>>>>

\subsection{Pool-Liquidierung}
\label{sec:pools-liquidierung}
\vspace{0.3cm}
\input{[B][Pools]/[Pools][Liquidierung]}    % binde die Datei '[Pools][Liquidierung].tex' ein

@@

%---------Pool-Economics------------------
\subsection{Pool-Economics}
\vspace{0.3cm}

\subsubsection{Einleitung}
\vspace{0.2cm}
\input{[B][Pools]/[Pools][Economic][Einleitung]}    % binde die Datei '[Pools][Economic][Einleitung].tex' ein
\vspace{0.5cm}

\subsubsection{WPT - Die grundlegende Idee eines Pools-Project-Utility-Tokens}
\vspace{0.2cm}
%\input{[B][Pools]/[Pools][Economic][WPT]}    % binde die Datei '[Pools][Economic][WPT].tex' ein
\input{[Pools][Economic][WPT]}
\vspace{0.5cm}

\subsubsection{Gebühren-Ordnung}
\label{sec:fees}
\vspace{0.2cm}
\input{[B][Pools]/[Pools][Economic][Fees]}    % binde die Datei '[Pools][Economic][Fees].tex' ein
\vspace{0.5cm}

\subsubsection{Business-Plan}
\vspace{0.2cm}
\input{[B][Pools]/[Pools][Economic][Business-Plan]}    % binde die Datei '[Pools][Economic][Business-Plan].tex' ein
\vspace{0.5cm}

\subsubsection{Herleitung Bonding-Curves}
\vspace{0.2cm}
\input{[B][Pools]/[Pools][Economic][Bonding-Curves]}    % binde die Datei '[Pools][Economic][Bonding-Curves].tex' ein
\vspace{0.5cm}

\input{[B][Pools]/[Pools][Economic][Rest]}    % binde die Datei '[Pools][Economic][Rest].tex' ein

\newpage
